Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-06-03 manuscript/Chapter2-manuscript.Rmd
other changes across methods and results. update section titles

All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2). The models were compiled on Cedar, a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar). The operating system for Cedar is CentOS Linux 7, and each model required 64GB of RAM with 48 cores to compile within $\le$5 days.

### Effect of experience on hunting success

We tested how prey influenced the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e. number of prey consumed) and the predators' cumulative experience (i.e. number of matches played before the current match). We parameterized the models following the method of @Pedersen.etal2019. The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID. In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e. global smoother). For the second model, we included varying individual smoothers for the predator ID. Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g. predator 1 has a steeper curve than predator 2). This enabled us to test whether predators differed in the development of their expertise. In the third model, we kept the individual smoothers for the predators, but removed the global smoother. This model assumes that predators do not share a common relationship between success and experience. The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience. We included the standardized match duration and prey rank as covariates in all five models.

We computed the five models using a modified version of the beta-binomial distribution implemented in "brms". Hunting success was estimated as the probability of consuming the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters. We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link. We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$). We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$). Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system. We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0, 0.5)$). We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

### Changes in foraging behaviour and predator-prey interactions with experience

@@

The model simultaneously estimated three distinct individual components for each trait across experience levels. The first component, estimated on the mean part of the model, is among individual variation in mean speed and success. This allows to test for individual differences in tactic use (i.e. along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption. The second component, estimated on the dispersion part of the model, is among individual variation in intra-individual variation (IIV). This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization . The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience. This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.

@@

where $j$ is the index of the experience levels. The model is fitted on the three experience levels denoted by $T_{j}$, where $j$ ranges from 1 to 3 (i.e. novice, intermediate, advanced). The $b$ terms are vectors of fixed effects with their design matrices $X$. The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$. The $d$ subscript indicates that a term is from the dispersion part of the model. For all experience levels of the predator and prey speed, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$). $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed. All the individual identity random effects (mean and dispersion) across all response variables and experience levels are indexed in vector $u$. The $u$ vector follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_i}$ across all experience levels and response variables.

We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn. 1.1 to 2.2) and game duration ($N(0.5,\ 0.5)$: eqn. 3). Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3, 0.5)$: eqn. 1.1 and 2.1). Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,1)$: eqn 1.2 and 2.2). For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn. 3) and a negative Gaussian prior ($N(-4, 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration. For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model. We used a regularizing $LKJ(2)$ prior on the correlation matrix.

@@

We parametrized both the GAMMs and the MDHMLM to run four MCMC chains with 1000 posterior samples for each parameter. We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models. We set the first 500 iterations in each model as warm ups. We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 iterations used as warm ups. We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@Vehtari.etal2021a]. We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics). We report all the posterior parameter estimates using the median of the posterior distribution with the highest posterior density (HPD) intervals at 50%, 80%, and 95%.

@@

## Effect of experience on hunting success

@@

# Open percentages table
path <- file.path(here::here("outputs", "03_outputs_model-processing"))
percent_tab1 <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))
```

Out of all five GAMM models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1). Predators differed substantially in the relationship between hunting success and cumulative experience (i.e. expertise: Figure 1A-B). We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B). For instance, many individual curves shifted upwards. Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A). In this model (i.e. Figure 1B-C), `r toString(scales::percent(percent_tab1[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab1[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).

Moreover, all models where we did not account for prey speed had a global trend of predator experience that was nearly flat (results not shown). Yet, we see that there is an increase up to 13% in the probability of consuming all prey with experience in the population when we account for prey speed (Figure 1C).

## Effect of experience on behavioural specialization and hunting success

The mean speed of the predator population did not change with experience (i.e. intercept (mean) of predator speed; Figure 2 and Appendix S1: Table S1). There was also strong evidence that foraging specialization in the population remained stable across experience levels (i.e. intercept (sigma) of predator speed; Figure 2 and Appendix S1: Table S1). We did not find evidence that the predator population had a change in mean success with experience (intercept (mean) of hunting success; Figure 2 and Appendix S1: Table S1). There was, however, a decrease in among individual differences in success at the intermediate stage, which was maintained at the advanced stage (predator ID (mean) of hunting success; Figure 2 and Appendix S1: Table S2).

Individual predators differed slightly in their mean speed across experience levels (i.e. predator ID (mean); Figure 2 and Appendix S1: Table S2). However, there was strong evidence that they displayed differences in foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced, indicating that differences increased slightly (i.e. predator ID (sigma) is higher at the advanced level; Figure 2 and Appendix S1: Table S2). Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3). Importantly, `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e. >0.2 change in standard deviation), `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation), while `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))`remained relatively stable (i.e. <0.05 change in standard deviation).

Contrary to predictions, there was strong evidence that predators did not differ in the mean speed of the prey groups that they encountered across experience (i.e. predator ID (mean); Figure 2 and Appendix S1: Table S2). However, individuals differed in the heterogeneity of the groups of prey encountered across the study period (i.e. predator ID (sigma); Appendix S1: Table S2). Hence, some predators encountered prey groups with similar mean speeds, while others encountered prey groups with varying mean speeds throughout the study period. The differences in the prey encountered among predators increased only slightly with experience (i.e. predator ID (sigma); Figure 2).

## Relationship between behavioural specialization and prey behaviour

Predators that were on average faster (mean speed) had a lower intra-individual variability (IIV speed) (Figure 4A-B and Appendix S4: Table S1). Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time. As predators gained experience, these strategies were increasingly defined as there was a 0.16 unit increase in the correlation at the advanced stage (Figure 4C). Predators that were on average faster (mean speed) also encountered groups of prey that were on average faster (mean prey speed) and more similar (IIV prey speed) (Figure 4A-B and Appendix S4: Table S1). There was however only weak to no evidence that these correlations increased with experience (Figure 4C)

@@

## Hunting success of behavioural specialists vs generalists

@@

**Figure 1.** Median posterior predictions of the development of predator hunting expertise. The predators' hunting success (i.e. the probability of consuming the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Panels A and C show among individual differences in the development of expertise, while panels B and D show the development of expertise for the average individual. (A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.

>>>>

All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2). The models were compiled on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar). Each required 64GB of RAM with 48 cores to compile within 5 days.

### Development of expertise

We tested how prey influenced the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e. number of prey consumed) and the predators' cumulative experience (i.e. number of matches played before the current match). We parametrized the models following the method of @Pedersen.etal2019. The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID. In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e. global smoother). For the second model, we included varying individual smoothers for the predator ID. Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g. predator 1 has a steeper curve than predator 2). This enabled us to test whether predators differed in the development of their expertise. In the third model, we kept the individual smoothers for the predators, but removed the global smoother. This model assumes that predators do not share a common relationship between success and experience. The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience. We included the standardized match duration and prey rank as covariates in all five models.

We computed the five models using a modified version of the beta-binomial distribution implemented in "brms". Hunting success was estimated as the probability of consuming the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters. We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link. We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$). We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$). Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system. We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5)$). We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

### Foraging behaviour and predator-prey interactions across experience

@@

The model simultaneously estimated three distinct individual components for each trait across experience levels. The first component, estimated on the mean part of the model, is among individual variation in mean speed and success. This allows to test for individual differences in tactic use (i.e. along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption. The second component, estimated on the dispersion part of the model by modeling the residuals, is among individual variation in intra-individual variation (IIV). This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization . The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience. This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.

@@

where $j$ is the index of the experience levels. The model is fitted on the three experience levels denoted by $T_{j}$, where $j$ ranges from 1 to 3 (i.e. novice, intermediate, advanced). The $d$ subscript indicates that a term is from the dispersion part of the model. The $b$ terms are vectors of fixed effects with their design matrices $X$. The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$. For all experience levels of the predator and prey speed, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$). $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed. All the individual identity random effects (mean and dispersion) across all response variables and experience levels are indexed in vector $u$. The $u$ vector follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_i}$ across all experience levels and response variables.

We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn. 1.1 to 2.2) and game duration ($N(0.5,\ 0.5)$: eqn. 3). Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5)$: eqn. 1.1 and 2.1). Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,\ 1)$: eqn 1.2 and 2.2). For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn. 3) and a negative Gaussian prior ($N(-4,\ 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration. For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model. We used a regularizing $LKJ(2)$ prior on the correlation matrix.

@@

We parametrized the GAMMs and the MDHGLM to run four MCMC chains with 1000 posterior samples for each parameter. We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models. We set the first 500 iterations in each model as warm ups. We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 iterations used as warm ups. We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@Vehtari.etal2021a]. We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics). We report all the posterior parameter estimates using the median of the posterior distribution with the highest posterior density (HPD) intervals at 50%, 80%, and 95%.

@@

## Development of expertise

@@

# Open percentages table
path <- file.path(here::here("outputs", "03_outputs_model-processing"))
percent_tab1 <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))

#fit1 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-rank.rds"))
#fit2 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-speed-rank.rds"))
#
#fit1
#fit2
```

Out of all five GAMM models, two predicted the data the best and achieved similar expected log pointwise densities (elpd). Both models accounted for the prey group's rank and speed (Table 1). Models in which these effects were not accounted for resulted in no change in hunting success with experience (i.e. expertise) for the average individual (results not shown). Accounting for the prey rank resulted in a concave-shaped relationship, with the highest success ranging between 100 and 400 matches (Figure 1A). In the model where we additionally included the prey's speed, the effect of experience on hunting success for the average individual followed a diminishing returns curve, with predators optimizing their success after playing ~300 matches (Figure 1C). The curve shows there was a 39% increase in the probability of consuming all prey for the average individual between the first and the 400$^{th}$ match which has the highest predicted success (Figure 1C).

The relationship between hunting success and cumulative experience differed among predators (Figure 1B and D). Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A). In contrast, accounting for both effects resulted in `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` of the population increasing its success with experience from the first match to the last. The prey speed alone also mediated individual differences in the relationship between success and experience. The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 ($95\%\ CI$: 9.30, 10.15), while the one for the model accounting for prey rank and speed was equal to 3.36 ($95\%\ CI$: 3.04, 3.71), indicating that individual differences in the development of expertise decreased when accounting for prey speed.

## Changes in foraging behaviour, prey behaviour, and hunting success

The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1). Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1). At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2). However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in IIV from novice to advanced (Figure 2). `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e. >0.2 change in standard deviation; Figure 3). In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` almost no change with experience (i.e. <0.05 change in standard deviation).

As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1). The population also encountered groups of prey using different speeds (Appendix S1: Table S1) which did not change with experience (Figure 2). At the individual level, all predators encountered prey with similar speeds on average throughout experience (Figure 2 and Appendix S1: Table S2). Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2). Thus, some predators encountered similar groups (i.e. all groups using similar speeds) while others encountered distinct groups (i.e. some slower and some faster). These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 2).

Similar to the GAMMs, the predator population's mean hunting success increased with experience (Figure 2 and Appendix S1: Table S1), with mean prey consumption revolving around two prey. There were also important differences among individuals in mean hunting success (Appendix S1: Table S2), but they remained stable across experience (Figure 2).

## Predator-prey interactions across experience

*je suis rendu ici*
Predators that were on average faster (mean speed) had a lower intra-individual variability (IIV speed) (Figure 4A-B and Appendix S4: Table S1). Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time. As predators gained experience, these strategies were increasingly defined as there was a 0.16 unit increase in the correlation at the advanced stage (Figure 4C). Predators that were on average faster (mean speed) also encountered groups of prey that were on average faster (mean prey speed) and more similar (IIV prey speed) (Figure 4A-B and Appendix S4: Table S1). There was however only weak to no evidence that these correlations increased with experience (Figure 4C)

@@

## Comparing the success of flexible and specialist foragers

@@

**Figure 1.** Median posterior predictions of the development of predator hunting expertise. The predators' hunting success (i.e. the probability of consuming the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Panels A and C show the development of expertise for the average individual with the vertical dashed lines representing the lowest and highest predicted values respectively. In contrast, panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator. (A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.

**Figure 2.** Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages. The behavioural parameter predicted by the MDHGLM being compared is on the y axis, and the difference in parameter values between two experience stages is on the x axis. The pairwise comparisons between experience stages are displayed across the three panels A, B, and C. We compare the mean speed of the predator population, the speed of the prey it encountered, and its hunting success across experience (population mean). We also compare the population's foraging specialization and variation in speed of the prey it encountered across experience (population variance). At the individual level, we compare among individual differences in speed, the speed of the prey encountered, and hunting success (individual variation mean). Lastly, we compare individual variation in IIV across experience, indicating whether individual differences in foraging specialization and in the variation of the groups of prey encountered changed with experience (individual variation IIV).
